---
title: "Interactive Apps — Bioconductor 2017"
subtitle: "Developer Day Workshop"
author: "Sean Davis"
date: "July 26, 2017"
output: 
  revealjs::revealjs_presentation:
    theme: night
    highlights: github    
---

<style type="text/css">
p { text-align: left; }
</style>

# Introduction
 
## R is great!

- Statistics, statistics, statistics
- Dataviz, dataviz, dataviz
- Highly reproducible data analysis environment and platform
- Broad and generous user and developer community
- Cross-platform development (now pretty common)

## But...

- R generally provides a highly personal experience, not a shared one
- Often, results exported to a static format for sharing
- Changing visualization or data presentation requires coding, sometimes limiting effectiveness as a data exploration platform
- Modern data science techniques leverage interactivity
- Very few standards for using R as a modern web framework

# Enter Shiny and Friends

## Single Page Applications

- gmail
- google docs
- online games
- many others....

https://en.wikipedia.org/wiki/Single-page_application

## Shiny Skeleton

```{r eval=FALSE}
library(shiny)

shinyApp(
    ###########################
    # The "server" function
    #   - Business goes here
    ###########################
    server = function(input,output,session) {
        
        # Do important work in here
        #   - read inputs
        #   - set up outputs
        
    },
    
    
    #########################################
    # and the "user interface"
    #   - Just displays user interface and
    #     provides interactivity features 
    #     and layout
    #########################################
    ui = fluidPage(
        titlePanel("title panel"),
        
        sidebarLayout(
            sidebarPanel("sidebar panel"),
            mainPanel("main panel")
        )
    )
)
```


## Shiny links

- layout: https://shiny.rstudio.com/articles/layout-guide.html
- DT for datatables: 
    - https://rstudio.github.io/DT/
    - https://rstudio.github.io/DT/extensions.html
    - https://rstudio.github.io/DT/shiny.html
- https://www.r-bloggers.com/the-r-shiny-packages-you-need-for-your-web-apps/

# Interactive graphics

## plotly

```{r eval=FALSE}
library(plotly)
data(diamonds)
p <- ggplot(data = diamonds, aes(x = carat, y = price)) +
  geom_point(aes(text = paste("Clarity:", clarity))) +
  geom_smooth(aes(colour = cut, fill = cut)) + facet_wrap(~ cut)

ggplotly(p)
```

## plotly

```{r echo=FALSE, warning=FALSE, message = FALSE}
library(plotly)
data(diamonds)
p <- ggplot(data = diamonds, aes(x = carat, y = price)) +
  geom_point(aes(text = paste("Clarity:", clarity))) +
  geom_smooth(aes(colour = cut, fill = cut)) + facet_wrap(~ cut)

ggplotly(p)
```

